\section{Conclusions}

Grouping key value pairs are essential for many practical applications that include MapReduce, SQL Hash Group By, etc. The volume of such data increases rapidly, therefore, it is essential to improve fast key value grouping methods. In this paper we proposed PowerHash, a method that supports very long records, large data sets and works efficiently even if the memory is very limited and is easily implemented. Extensive experimental evaluation with real data sets whose group sizes follow the power-law distributions revealed that our method is much more efficient than existing ones in terms of speed and computational resources, it can reduce the repeat access to disk caused by the distribution unbalance effectively when grouping these data sets. When the available is limited, our algorithm runs faster than merge-sort and memory-constraint hash with the same memory. The merge-sort and memory-constraint hash need several times memory to achieve the best state compared to our algorithm, it can help us save a large amount of memory when executing key grouping operation. This work is part of a large project that aims to develop an engine for grouping and processing of massive data. We are currently working on scaling our method to the distributed computing framework. As we know, stand-alone aggregating key value pairs of different groups is applied to both map phase and reduce phase in MapReduce independently. So PowerHash is easily parallelizable. We are also focusing on the parallel processing various types of grouping using the PowerHash.

